Synthetic Observations of Extremely High Velocity (EHV) SiO component in young molecular outflows

### 2013-12-15 PAPER/Paola_2/ms_ver3.tex
Captions done and new figs in paper

 \begin{figure}
  \includegraphics[width=1.\columnwidth]{\figpath/pfig3.pdf}%{\figpath/diffabun_profnew.png}
  \caption{{\bf{CHANGEFIG}} The different fractional SiO abundances as a function of
    jet velocity, v$_{\rm jet}$.}
  \label{abun}
 \end{figure}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig5.pdf}%diffcool_img.pdf}
 \caption{A plot of the integrated SiO J=2-$>$1 emission from 5 models, 
each using a different method to calculate cooling and all with $\eta$=10.}
\label{fig:coolcmpsio} 
\end{figure*}

@@

\begin{figure}
 \includegraphics[width=1.\columnwidth]{\figpath/pfig6.pdf}%hfracs_ref.pdf}
 \caption{{\it{Left}} Color composite image of various hydrogen
   fractions, fHI (red), fH$_{2}$ (green) and fHII (blue), for the
   reference run. For better visualisation, the ionized hydrogen
   fraction is enhanced by a factor of 100. The temperature of the jet
 obtained from dynamical simulation is shown on the {\it{right}}.}
\label{fig:Hfracsim}
\end{figure}

The distribution of fractions of different hydrogen species along with
temperature suggests that there are essentially three regions where
chemistry is evolved due to shocks.
They are : (1) The tip of the jet , (2) The edges of the jet and
(3) intermediate knots. 
As the atomic jet propagates from the lower boundary 
into the cold molecular medium , it forms a strong shock resulting in
forming a density and temperature discontinuity. Such a jump in
dynamical quantities plays a crucial role in the evolution of
chemistry. For example, temperatures beyond few 1000\,K produced in the shocks could
disassociate the molecules and can also lead to ionization if
the temperature becomes larger than 10$^{4}$\,K.
%
\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig7.pdf}%molcjet_310_molform.pdf}
 \caption{Dependence of hydrogen fractions on the temperature at two
   points in the flow, viz. the interface of the knot with molecular
   medium and at the bow shock.}
\label{fig:Hmolform}
\end{figure*}

@@

\begin{figure}
 \includegraphics[width=1.\columnwidth]{\figpath/pfig8.pdf}%emspecpv_90.pdf}%{\figpath/refrun_21_90_emspecpv.png}
 \caption{Integrated emission map ({\it top left}), PV diagram ({\it top right}
   and spectra ({\it bottom}) for the
   2-$>$1 SiO transition for the reference run. 
   The jet is assumed to be in the plane of sky implying an angle of
   inclination of $90^{\circ}$. The vertical {\it magenta dashed} line
   represents the cut for the PV digram and green crosses marks the positions from which the spectra are taken.} 
\label{empvspec90}
\end{figure}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig10.pdf}%diffabun_img.pdf}%{\figpath/EM_gaussandth.png}
 \caption{Variation of 2-$>$1 SiO emission for runs with molecular
   cooling having different abundance profiles.}
\label{fig:diffabunem}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig11.pdf}%diffabun_PV.pdf}%{\figpath/PV_gaussandth.png}
 \caption{Position-velocity maps of SiO(2-1) for the internal
   knots produced in the model with reference parameters and different abundance
   profiles. The contours mark different levels of emission in Kelvins, viz.,
   0.2,0.6,1.0,1.4,1.8,2.0,3.0,4.0.}
\label{fig:pvdiffabun}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig12_temp.pdf}%almamaps_new.pdf}%{\figpath/ALMAmaps3.png}
 \caption{{\bf Left:} The integrated intensity map of SiO(2-1), (5-4)
   and (8-7). The emission map shows the 5-4 line intensity (in units
   of Jy$\,$kms$^{-1}$/beam), the blue contours show the J=8-7 line
   intensity and the green contours show the J=2-1 line intensity. The
   jet is inclined at an angle of 60$^{\circ}${\bf Right:} The PV
   diagram taken along the axis of the jet for the 5-4 line (in units
   of Jy/beam), showing the higher J transitions highlighting the
   knots of the jet and broad emission at the bow shock. 
   In both panels the ticks on the color bar represent the different contour levels.}
\label{fig:almafig}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig13.pdf}%imshkvhcontomaps.png}
 \caption{Symmetrical contour maps of multi-line integrated SiO
   emission convolved with a 2\arcsec beam obtained using parameters of the reference run. The contour colors represent different intenties in Kelvins, i.e,
   20.0({\it red}), 10.0({\it green}), 5.0({\it blue}), 1.0({\it
     magenta}), 0.5({\it cyan}), 0.1({\it black}).} 
\label{fig:ltconts}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig14.pdf}%singledish_new.pdf}%{\figpath/LineRatio_THDeq1.png}
 \caption{{\em{Top}} Line profiles in SiO (2-1), (5-4) and (8-7) at one
   the inner knots for the reference molecular cooling run with a top
   hat abundance profile and $\delta = 1$. The profiles are
   obtained when the angle of inclination is 60$^{\circ}$ with respect
 to line of sight. {\em{Bottom left}} Line intensity ratios SiO(8-7)/(5-4)
and SiO(5-4)/(2-1), as a function of velocity. {\em{Bottom right}}
Variation of integrated intensity with upper line transition J$_{\rm
  up}$ for two abundance profiles.}
\label{fig:lineratio}
\end{figure*}

@@

The variation of SiO abundance used for the present model is rather
obtained from empirical values. In case of L1448, \cite{MartinPintado:1992p14309}
have shown that for extreme velocities (obtained from shift in the
spectra) of -40 to -50 km\,s$^{-1}$, the SiO abundance could be as
large as $6\times10^{-7}$, while, it slightly increases to
$2\times10^{-6}$ for the velocity range of -60 to -50
km\,s$^{-1}$. For the same source, typical {\em{shock}} (or working
surface) velocities of the {\em{molecular bullets}} are estimated to
lie around 80-175 km\,s$^{-1}$ \cite{Dutrey:1997p11185}.
\\
{\color{red}
WE HAVE TWO OPTIONS:\\ 
1. Since the there is a empirical evidence with bulk gas motion. We
can use just the jet velocity obtained from simulations.\\
OR\\
2. We can try to connect the working surface velocities from
\cite{Dutrey:1997p11185} to abundance obtained by
\cite{MartinPintado:1992p14309} and there by use the velocity of the
working surface as an independent variable on the X axis of the
abundance plot.
}

>>>>

 \begin{figure}
  \includegraphics[width=1.\columnwidth]{\figpath/pfig3.pdf}%{\figpath/diffabun_profnew.png}
  \caption{The different fractional SiO abundances as a function of
    jet velocity, v$_{\rm jet}$.}
  \label{abun}
 \end{figure}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig5.pdf}%diffcool_img.pdf}
 \caption{A plot of the integrated SiO(2-1) emission from 5 models, 
each using a different method to calculate cooling and all with $\eta$=10.}
\label{fig:coolcmpsio} 
\end{figure*}

@@

\begin{figure}
 \includegraphics[width=1.\columnwidth]{\figpath/pfig6.pdf}%hfracs_ref.pdf}
 \caption{{\it{Left}}: Color composite image of various hydrogen
   fractions, fHI (red), fH$_{2}$ (green) and fHII (blue), for the
   reference run. For better visualisation, the ionized hydrogen
   fraction is enhanced by a factor of 100. The temperature of the jet
 obtained from dynamical simulation is shown on the {\it{right}}.}
\label{fig:Hfracsim}
\end{figure}

The distribution of fractions of different hydrogen species along with
temperature suggests that there are essentially three regions where
chemistry is evolved due to shocks.
They are : (1) The tip of the jet , (2) The edges of the jet and
(3) intermediate knots. 
As the atomic jet propagates from the lower boundary 
into the cold molecular medium , it forms a strong shock resulting in
forming a density and temperature discontinuity. Such a jump in
dynamical quantities plays a crucial role in the evolution of
chemistry. For example, temperatures beyond few 1000\,K produced in the shocks could
disassociate the molecules and can also lead to ionization if
the temperature becomes larger than 10$^{4}$\,K.
%
\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig7.pdf}%molcjet_310_molform.pdf}
 \caption{{\textit{Top}}: Number density, n$_\rm H$ [cm$^{-3}$], obtained from the reference run along with labels of typical jet features.{\textit{Bottom}}: Dependence of hydrogen fractions on the temperature at two
   points in the flow, viz. the interface of the knot ({\it{left}}) with molecular
   medium and at the bow shock ({\it{right}}).}
\label{fig:Hmolform}
\end{figure*}

@@

\begin{figure}
 \includegraphics[width=1.\columnwidth]{\figpath/pfig8.pdf}%emspecpv_90.pdf}%{\figpath/refrun_21_90_emspecpv.png}
 \caption{Integrated emission map ({\it top left}), PV diagram ({\it top right}
   and spectra ({\it bottom}) for the
   SiO(2-1) transition for the reference run. 
   The jet is assumed to be in the plane of sky implying an angle of
   inclination of $90^{\circ}$. The vertical {\it magenta dashed} line
   represents the cut for the PV digram and {\it green} crosses marks the positions from which the spectra are taken.} 
\label{empvspec90}
\end{figure}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig10.pdf}%diffabun_img.pdf}%{\figpath/EM_gaussandth.png}
 \caption{Variation of SiO(2-1) emission for runs with molecular
   cooling having different abundance profiles.}
\label{fig:diffabunem}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig11.pdf}%diffabun_PV.pdf}%{\figpath/PV_gaussandth.png}
 \caption{Position-velocity maps of SiO(2-1) for the internal
   knots produced in the model with reference parameters and different abundance
   profiles. The contours mark different levels of emission in Kelvins, viz.,
   0.1,0.2,0.6,1.0,1.4,1.8,2.0,3.0,4.0.}
\label{fig:pvdiffabun}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig12_temp.pdf}%almamaps_new.pdf}%{\figpath/ALMAmaps3.png}
 \caption{{\bf Left:} The integrated intensity map of SiO(2-1), (5-4)
   and (8-7). The emission map shows the J=5-4 line intensity (in units
   of Jy$\,$kms$^{-1}$/beam), the blue contours show the J=8-7 line
   intensity and the green contours show the J=2-1 line intensity. The
   jet is inclined at an angle of 60$^{\circ}${\bf Right:} The PV
   diagram taken along the axis of the jet for the 5-4 line (in units
   of Jy/beam), showing the higher J transitions highlighting the
   knots of the jet and broad emission at the bow shock. 
   In both panels the ticks on the color bar represent the different contour levels.}
\label{fig:almafig}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig13.pdf}%imshkvhcontomaps.png}
 \caption{Symmetrical contour maps of multi-line integrated SiO
   emission convolved with a 2\arcsec beam obtained using parameters of the reference run. The contour colors represent different intensities in Kelvins, i.e, 50.0({\it red}), 30.0({\it green}), 20.0({\it blue}), 5.0({\it
     magenta}), 2.0({\it cyan}), 0.1({\it black}).} 
\label{fig:ltconts}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig14.pdf}%singledish_new.pdf}%{\figpath/LineRatio_THDeq1.png}
 \caption{{\em{Top}}: Line profiles in SiO (2-1), (5-4) and (8-7) at one
   the inner knots for the reference molecular cooling run. The profiles are
   obtained when the angle of inclination is 60$^{\circ}$ with respect
 to line of sight. {\em{Bottom left}}: Line intensity ratios SiO(8-7)/(5-4)
and SiO(5-4)/(2-1), as a function of velocity. {\em{Bottom right}}:
Variation of normalised integrated intensity with upper line transition J$_{\rm
  up}$ for the reference run.}
\label{fig:lineratio}
\end{figure*}

@@

The variation of SiO abundance used for the present model is rather
obtained from empirical values. In case of L1448, \cite{MartinPintado:1992p14309}
have shown that for extreme velocities (obtained from shift in the
spectra) of -40 to -50 km\,s$^{-1}$, the SiO abundance could be as
large as $6\times10^{-7}$, while, it slightly increases to
$2\times10^{-6}$ for the velocity range of -60 to -50
km\,s$^{-1}$. For the same source, typical {\em{shock}} (or working
surface) velocities of the {\em{molecular bullets}} are estimated to
lie around 80-175 km\,s$^{-1}$ \cite{Dutrey:1997p11185}.

%\\
%{\color{red}
%WE HAVE TWO OPTIONS:\\ 
%1. Since the there is a empirical evidence with bulk gas motion. We
%can use just the jet velocity obtained from simulations.\\
%OR\\
%2. We can try to connect the working surface velocities from
%\cite{Dutrey:1997p11185} to abundance obtained by
%\cite{MartinPintado:1992p14309} and there by use the velocity of the
%working surface as an independent variable on the X axis of the
%abundance plot.
%}
